\section{Specifications}
The following specifications are the most basic requirements of what the Hyperloop pod must do. Here we set out everything that relates to the software and electronics.


\subsection{Sensing}
\begin{enumerate}
    \item The system must be able to know its location (relative to the length of the Hyperloop track) with a tolerance of less than 0.2m.
    \item The system must be able to know its distance from the rails with a tolerance of less than 1mm.
    \item The system must be able to validate that a sensor is alive and performing as intended.
    \item The system must be able to show the properties and status from any selected sensor.
    \item The system must be able to show, in real time, readings from any selected sensor.
    \item The System must be able to detect and try to correct any erroneous sensor readings.
\end{enumerate}

\subsection{Dynamics}
\begin{enumerate}
    \item The system must be able to dynamically brake depending on its environment and current location in order to maintain control.
    \item The system must accelerate depending on its environment and current location so that the highest possible speed is achieved.
    \item The system must be able to perform an emergency stop when requested.
    \item The system must be able to reach and maintain a selected speed quickly and reliably.
    \item 
\end{enumerate}

\subsection{Communication}
\begin{enumerate}
    \item The system must be able to perform wireless communication with an external device.
    \item The system must have some form of remotely-connected GUI that allows users to modify internal system settings.
\end{enumerate}

\subsection{Navigation}
\begin{enumerate}
    \item The pod must be able to travel to a given location on the Hyperloop track unsupervised and arrive safely at its destination.c+
\end{enumerate}

\subsection{Logging}
\begin{enumerate}
    \item The system must log all key events such that simulated replay is possible.
    \item Log when and why a process exits.
    \item Log when and how long it took for a given process to start up.
    \item Log notable events during the operation of the software.
    \item Regularly log sensor data at a rate of 10 Hz.
The user must be able to easily retrieve the logs
The format of all logged message must be uniform to allow the user to easily read the log
Logged data must actually be recorded
Sensitive data must only be logged securely
\end{enumerate}

\subsection{Remote Access}
\begin{enumerate}
    \item The system must be able to receive new firmware and software over the air.
    \item The system must be able to read and write settings to a permanent location so that any changes can be recovered on system restart.
    \item The system must maintain a constant state between all GUIs that are connected simultaneously
    \item The system must continue stop if a user unexpectedly disconnects
\end{enumerate}

\subsection{System Reliability}
\begin{enumerate}
    \item All services must be constantly up - any abnormal exits from a program must be logged and restarted.
    \item The system must recover from a misbehaviour in the software/hardware.
\end{enumerate}
